---
title: "hw5_ss7636"
output: html_document
date: "2025-11-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(broom)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```


Problem 1
```{r}
bday_sim = function(n_room) {
  birthdays = sample(1:365, n_room, replace = TRUE)
  repeated_bday = length(unique(birthdays)) < n_room
  repeated_bday
}
```

```{r}
bday_sim_results =
  expand_grid(
    bdays = 2:50,
    iter = 1:10000
  ) |> 
  mutate(
    result = map_lgl(bdays, bday_sim)
  ) |> 
  group_by(
    bdays
  ) |> 
  summarize(
    prob_repeat = mean(result)
  )

bday_sim_results

```

```{r}
bday_sim_results |> 
  ggplot(aes(x = bdays, y = prob_repeat)) +
  geom_point() +
  geom_line()
```

We can see that the probability of getting a repeat birthday exponentially increases as the number of students starts to increase, which makes sense. The probability is almost 0 at 2 students and the probability is almost 1 at 50 students.

Problem 2

```{r}
n = 30
sigma = 5
mu = 0:6
n_sim = 5000
alpha = 0.05

results = expand_grid(mu = mu, sim = 1:n_sim) |> 
  mutate(
    data = map(mu, ~rnorm(n, mean = .x, sd = sigma)),
    ttest = map(data, ~ broom::tidy(t.test(.x, mu = 0)))
  ) |> 
  unnest(ttest) |> 
  select(mu, estimate, p.value)

summary_results = results |> 
  group_by(mu) |> 
  summarize(
    power = mean(p.value < alpha),
    mean_est = mean(estimate),
    mean_est_rejected = mean(estimate[p.value < alpha])
  )
```

```{r}
ggplot(summary_results, aes(x = mu, y = power)) +
  geom_line() +
  geom_point() +
  labs(
    x = "True Mean (μ)",
    y = "Power",
    title = "Power Increases with Effect Size"
  ) 
```
As the true mean increases, power increases. When the true mean is 0, the power is around 0.05. When the true mean reaches around 5, the power is 1.


```{r}
summary_results |> 
  ggplot(aes(x = mu)) +
  geom_line(aes(y = mean_est), color = "black") +
  geom_line(aes(y = mean_est_rejected), color = "red", linetype = "dashed") +
  geom_point(aes(y = mean_est), color = "black") +
  geom_point(aes(y = mean_est_rejected), color = "red") +
  labs(
    x = "True Mean (μ)",
    y = "Average Estimated Mean (μ̂)",
    title = "Bias of Estimates When Selecting Only Significant Results",
    subtitle = "Black = all samples, Red = only significant (p < 0.05)"
  ) 
```

The average estimated mean is are slightly larger than the true mean, especially as the true mean is less than 3. They start to become more equal as the true mean increases. This might be because only unusually large estimates (due to sampling variability) cross the significance threshold.

Problem 3

```{r}
homicide = 
 read_csv("homicide-data.csv", na = c("NA",".", "")) |> 
  janitor :: clean_names() 
homicide
```

This dataset contains 52,179 rows and 12 columns. This data contains The data included the location of the killing, date of the report, whether an arrest was made and, basic demographic information about each victim.

```{r}
homicide_city_state = 
  homicide |> 
  mutate(
    city_state = paste(city, state, sep = ", ")
  )
homicide_city_state
```

```{r}
city_summary = homicide_city_state |>
  mutate(
    unsolved = disposition %in% c("Closed without arrest", "Open/No arrest")
  ) |> 
  group_by(city_state) |> 
  summarize(
    total = n(),
    unsolved_count = sum(unsolved),
    .groups = "drop"
  )

city_summary
  
```

```{r}
baltimore_test <- 
  city_summary |> 
  filter(city_state == "Baltimore, MD") |>  
  summarize(test = list(prop.test(unsolved_count, total))) |>  
  pull(test) |>
  (\(x) broom::tidy(x[[1]]))() |>
  select(estimate, conf.low, conf.high) 

baltimore_test
```

```{r}
city_props = city_summary |> 
  mutate(
    prop_test = map2(unsolved_count, total, ~ prop.test(.x, .y) |> 
                       broom :: tidy())
  ) |> 
  unnest(prop_test) |> 
  select(city_state, estimate, conf.low, conf.high)

city_props
```

```{r city-plot, fig.height=100, fig.width=10}
city_props |> 
  arrange(desc(estimate)) |> 
  mutate(city_state = factor(city_state, levels = city_state)) |> 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  coord_flip() +
  labs(
    x = "City",
    y = "Proportion of Unsolved Homicides",
    title = "Estimated Proportion of Unsolved Homicides by City"
  ) 
```

